Bioverse: Origins of Life

### 2024-06-22 src/tex/ms.tex
make multipanel figs wide
number and explain example planet tracks

%! suppress = GroupedSubSupScript
%! suppress = Ellipsis
% Define document class
%\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
\documentclass[modern,linenumbers]{aastex631}
\input{preamble}
%! suppress = LineBreak
\begin{document}

@@

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. The scatter plot shows age and host star mass of the transiting planets in the synthetic sample.% with \gls{EEC} highlighted in green.
        We show the evolutionary tracks of a few randomly selected planets.
        Tracks with extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections) fulfill our requirement for abiogenesis.}
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \script{semian_true_evidence.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/semian_selectivity}
        \caption{Scaling of the probability of obtaining true strong evidence with sample selectivity. Left: Sampling distribution for different selectivity parameters $s$. Right: Resulting \mbox{P(true strong evidence)} (random, uniform $f_\mathrm{life}$, $F_\mathrm{NUV, min}$). Sampling more extreme values of $F_\mathrm{NUV}$ is more likely to yield strong evidence.}
        \label{fig:semian_selectivity}
    \end{centering}
\end{figure}

@@

\subsubsection{Selectivity of simulated transit surveys}
In Section~\ref{sec:results-semianalytical}, we demonstrated that the probability of obtaining true strong evidence for the hypothesis that life only originates on planets with a minimum past \gls{NUV} flux is sensitive to the distribution of sampled past \gls{NUV} fluxes, i.e., the selectivity of the survey (compare Figure~\ref{fig:semian_selectivity}).
%The maximum \gls{NUV} distribution of our generic transit survey is rather unimodal with a median around \SI{500}{\erg\per\second\per\centi\meter\squared} (see Figure~\ref{fig:nuv_distribution}), leading to a selectivity of roughly \var{selectivity_transit_volumelim}.
For both surveys targeting M dwarfs and those targeting FGK dwarfs, the maximum \gls{NUV} distribution is rather unimodal.
Applying the approach from Sect.~\ref{sec:results-semianalytical} of fitting a Beta function to the distribution, we find rather low selectivities (see Figure~\ref{fig:nuv_distribution}).
\begin{figure}
    \script{nuv_distribution.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/nuv_distribution}
        \caption{Distribution of maximum past \gls{NUV} flux in transit surveys targeting FGK and M~stars, respectively. The best-fit beta distributions (gray) correspond to selectivities of $s_\mathrm{FGK} = $\var{selectivity_FGK} and $s_\mathrm{M} = $\var{selectivity_M}.}
        \label{fig:nuv_distribution}
    \end{centering}
\end{figure}

\subsubsection{Expected biosignature pattern in a transit survey}
A representative recovery of the injected biosignature pattern is shown in Figure~\ref{fig:detections_uv}.
There, we assumed an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a minimum \gls{NUV} flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$.
All injected biosignatures are assumed to be detected, and the maximum \gls{NUV} flux is estimated from the host star's spectral type and age with an uncertainty corresponding to the intrinsic scatter in the \gls{NUV} fluxes in \citet{Richey-Yowell2023}.
\begin{figure}
    \script{detections_uv.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/detections_uv}
        \caption{Recovered biosignature detections in the \gls{NUV} flux -- biosignature occurrence space. The dashed line denotes a generic threshold \gls{NUV} flux $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$.}
        \label{fig:detections_uv}
    \end{centering}
\end{figure}
This leads to a distribution of biosignature detections with detections increasingly occurring above a threshold inferred NUV flux.
In this example case, the few biosignature detections in the FGK sample lead to a higher evidence ($dlnZ_\mathrm{FGK} = \var{dlnZ_FGK}$) than in the M dwarf sample ($dlnZ_\mathrm{M} = \var{dlnZ_M}$), where the majority of planets are above the threshold \gls{NUV} flux.

@@

\begin{figure}
    \script{powergrid.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/powergrid}
        \caption{Statistical power as a function of threshold \gls{NUV} flux and abiogenesis rate. For a given sample size (here: $N=\var{N_nautilus}$), the achieved statistical power of the survey is enhanced for higher values of $f_\mathrm{life}$ and intermediate values of $F_\mathrm{NUV, min}$.}
        \label{fig:powergrid}
    \end{centering}
\end{figure}

>>>>

%! suppress = GroupedSubSupScript
%! suppress = Ellipsis
% Define document class
%\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
\documentclass[modern,linenumbers]{aastex631}

\input{preamble}
%! suppress = LineBreak
\begin{document}

@@

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. The scatter plot shows age and host star mass of the transiting planets in the synthetic sample. % with \gls{EEC} highlighted in green.
        A few example tracks are shown, where extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections) fulfill our requirement for abiogenesis.
        Planet~1 is an \gls{EEC} that never receives sufficient \gls{NUV} flux for abiogenesis.
        Planet~2 and Planet~3 enter the \gls{HZ} at different times and receive sufficient \gls{NUV} flux for different durations until their respective host star evolves below the threshold.
        }
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

\begin{figure*}
    \script{semian_true_evidence.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/semian_selectivity}
        \caption{Scaling of the probability of obtaining true strong evidence with sample selectivity. Left: Sampling distribution for different selectivity parameters $s$. Right: Resulting \mbox{P(true strong evidence)} (random, uniform $f_\mathrm{life}$, $F_\mathrm{NUV, min}$). Sampling more extreme values of $F_\mathrm{NUV}$ is more likely to yield strong evidence.}
        \label{fig:semian_selectivity}
    \end{centering}
\end{figure*}

@@

\subsubsection{Selectivity of simulated transit surveys}
In Section~\ref{sec:results-semianalytical}, we demonstrated that the probability of obtaining true strong evidence for the hypothesis that life only originates on planets with a minimum past \gls{NUV} flux is sensitive to the distribution of sampled past \gls{NUV} fluxes, i.e., the selectivity of the survey (compare Figure~\ref{fig:semian_selectivity}).
%The maximum \gls{NUV} distribution of our generic transit survey is rather unimodal with a median around \SI{500}{\erg\per\second\per\centi\meter\squared} (see Figure~\ref{fig:nuv_distribution}), leading to a selectivity of roughly \var{selectivity_transit_volumelim}.
For both surveys targeting M dwarfs and those targeting FGK dwarfs, the maximum \gls{NUV} distribution is rather unimodal.
Applying the approach from Sect.~\ref{sec:results-semianalytical} of fitting a Beta function to the distribution, we find rather low selectivities (see Figure~\ref{fig:nuv_distribution}).
\begin{figure*}
    \script{nuv_distribution.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/nuv_distribution}
        \caption{Distribution of maximum past \gls{NUV} flux in transit surveys targeting FGK and M~stars, respectively. The best-fit beta distributions (gray) correspond to selectivities of $s_\mathrm{FGK} = $\var{selectivity_FGK} and $s_\mathrm{M} = $\var{selectivity_M}.}
        \label{fig:nuv_distribution}
    \end{centering}
\end{figure*}

\subsubsection{Expected biosignature pattern in a transit survey}
A representative recovery of the injected biosignature pattern is shown in Figure~\ref{fig:detections_uv}.
There, we assumed an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a minimum \gls{NUV} flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$.
All injected biosignatures are assumed to be detected, and the maximum \gls{NUV} flux is estimated from the host star's spectral type and age with an uncertainty corresponding to the intrinsic scatter in the \gls{NUV} fluxes in \citet{Richey-Yowell2023}.
\begin{figure*}
    \script{detections_uv.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/detections_uv}
        \caption{Recovered biosignature detections in the \gls{NUV} flux-biosignature occurrence space. The dashed line denotes a generic threshold \gls{NUV} flux $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$.}
        \label{fig:detections_uv}
    \end{centering}
\end{figure*}
This leads to a distribution of biosignature detections with detections increasingly occurring above a threshold inferred NUV flux.
In this example case, the few biosignature detections in the FGK sample lead to a higher evidence ($dlnZ_\mathrm{FGK} = \var{dlnZ_FGK}$) than in the M dwarf sample ($dlnZ_\mathrm{M} = \var{dlnZ_M}$), where the majority of planets are above the threshold \gls{NUV} flux.

@@

\begin{figure*}
    \script{powergrid.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/powergrid}
        \caption{Statistical power as a function of threshold \gls{NUV} flux and abiogenesis rate. For a given sample size (here: $N=\var{N_nautilus}$), the achieved statistical power of the survey is enhanced for higher values of $f_\mathrm{life}$ and intermediate values of $F_\mathrm{NUV, min}$.}
        \label{fig:powergrid}
    \end{centering}
\end{figure*}
